Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-10-28 Tex/Old text/chapters/conclusion.tex
Thesis update

Concerning the first contribution presented in ~\autoref{chap:automatedverification}, we described and evaluated an automated verification method to validate a given stand-alone PV system design and check whether it meets its user and electrical requirements using software model checking techniques.  There exist various possibilities to perform that validation, such as testing, laboratory measuring, or even simulation (used before field deployment, as our proposal). \textcolor{red}{this sentence is unclear....} However, we showed, supported by an algorithm that uses our approach, moreover supported by case studies, by monitoring data from field, and from an interview with the owners, that our approach is feasible and effective.

@@

Moreover, it was not necessary to ``adapt'' the tool, since the specialized simulation tool (HOMER Pro) had to be adjusted in order not to perform the optimization of the system. \textcolor{red}{this sentence is unclear...} Besides, only the proposed method of automated verification was possible to validate a system with a specific battery autonomy, since HOMER Pro does not have this feature.

%In a nutshell, our proposed PV system validation method, who check the size of inputted PV system, and verifies it over the time, was feasible and effective, supported by a algorithm written to implement the method, by a comparative with a commercial simulation tool, and by real data collect at the field.
%
\textcolor{red}{this sentence needs to be rewritten... when you use better, less, etc, you need to use ``than'' and add the second sentence for the comparison.}
Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the 'incremental SMT' configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than $2$ GB when compared to $9.2$ GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presented in the field.
%New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study.

@@

\textcolor{red}{These sentences are too long and difficult to understand.}
We proposed a variant of CEGIS synthesis process, working with just one feasible solution from the {\sc Synthesize} phase, and a refinement from the iterative search from the {\sc Verify} phase, which allows the optimization of stand-alone PV systems with the best compromise between power reliability and system cost analysis. Our algorithm that implements this method uses a database of commercial equipment from the marketing, including the price. In order to validate our proposed method, we considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker), in addition to a specialized off-the-shelf simulation tool (HOMER Pro) to compare the results. In terms of performance and better results, CPAchecker was the winner and used for the comparative with the simulation tool.

@@

\textcolor{red}{This sentence is too long and difficult to understand.}
It is planned to develop the code of a general-purpose simulation tool, using the same mathematical model employed for the model checking methods of this work, to include it in the comparative in order to cover all the possibilities to validate or optimize solar PV systems.

@@

\textcolor{red}{This sentence is too long and difficult to understand.}
The automated verification and automates synthesis methods demonstrate the effectiveness and the potential of use in stand-alone solar PV systems. Some issues must be addressed in order to improve the tools, as performance and the human-computer interaction. However, the work has potential, and it is promising \textcolor{red}{how is it promising?}.

\textcolor{red}{This sentence is too long and difficult to understand.}
About license and the use of tools that the author employed at this work, must be noticed that HOMER Pro is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}; the verifiers, as CPAchecker, ESBMC and CBMC, and their solvers, they are based on open-source software license and usually allows the users to use, modify, and distribute licensed product freely. Permission is granted, free of charge, to use this software for evaluation and research purposes (and that is an advantage when compared to commercial tools); therefore, some of the licenses do not allow the software to be used in a commercial context.

@@

\textcolor{red}{this sentence is tool informal with the use of ``you''.}
And last, but not least significant to report, besides the fact that the goal of a PhD is to contribute to the body of human research, one of the great things about PhD is you will be able to conduct your research. In that direction, we can say that with the technique proposed here (formal methods using automated verification and model checking) to energy sector, there exists a vast field of future applications and developments, using different renewable sources, as biomass, wind, or even hybrid, with different mathematical models and requirements; and including smart grids, or electrical systems in general. Few research has been done until now, and the scenario is auspicious from now on.

>>>>

Concerning the first contribution presented in ~\autoref{chap:automatedverification}, we described and evaluated an automated verification method to validate a given stand-alone PV system. \textcolor{red}{Our method, using model checking, can performance size check and verify, over time, if a PV system meets electrical requirements. We showed that there exist various possibilities to perform that validation, such as testing, laboratory measuring, or even simulation. However, we developed an algorithm and a tool using model checking that was feasible and effective. Our results were supported by case studies, by monitoring data from field, and from an interview with PV owners.}

@@

\textcolor{red}{Moreover, considering that HOMER Pro always perform size optimization during the simulation process, the user always have to 'adapt' this simulation tool in order to avoid the optimization and to validate the PV system as inputted in it. That adaptation is not necessary using our approach, because optimization is another method different of verification. Besides, only the proposed method of automated verification was possible to validate a system with a specific battery autonomy, since HOMER Pro does not have this feature, i.e., the user can not specify the battery autonomy.}

%In a nutshell, our proposed PV system validation method, who check the size of inputted PV system, and verifies it over the time, was feasible and effective, supported by a algorithm written to implement the method, by a comparative with a commercial simulation tool, and by real data collect at the field.
%
\textcolor{red}{Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the 'incremental SMT' configuration presented the better performance than CBMC (around four times faster), used less RAM memory than CBMC and CPAchecker (less than $2$ GB when compared to $9.2$ GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presented in the field.}
%New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study.

@@

\textcolor{red}{We proposed a variant of CEGIS synthesis process, working with just one feasible solution from the {\sc Synthesize} phase, and a refinement from the iterative search from the {\sc Verify} phase. With this approach, we obtain optimization of stand-alone PV systems with the best compromise between power reliability and system cost analysis. Our algorithm, that implements this method, uses a database of commercial equipment from the marketing, including the price. Furthermore, in order to validate our method, we considered seven case studies from PV systems in two different sites of the Amazonas State in Brazil, ranging from $253$\,W to $1,586$\,W peak; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker). In addition, we used again the specialized off-the-shelf simulation tool (HOMER Pro) to compare the results. In terms of performance and better results, CPAchecker was the winner and used for the comparative with the simulation tool. }

@@

\textcolor{red}{It is planned to develop the code of a general-purpose simulation tool, as MATLAB for example, using the same mathematical model employed in our two methods. Thus a broader comparison can be made, in order to cover all the possibilities to validate or optimize solar PV systems.}

@@

\textcolor{red}{The automated verification and automates synthesis methods demonstrate the effectiveness and the potential of use in stand-alone solar PV systems. Some issues must be addressed in order to improve the tools, as performance and the human-computer interaction.}.

\textcolor{red}{About license and the use of tools mentioned in this thesis, must be noticed that HOMER Pro is available only for Microsoft Windows and its annual standard subscription costs US\$ $504.00$~\cite{HOMER}. Related to the verifiers, as CPAchecker, ESBMC and CBMC, and their solvers, they are based on open-source software license and usually allows the users to use, modify, and distribute licensed product freely. Permission is granted, free of charge, to use this software for evaluation and research purposes (and that is an advantage when compared to commercial tools).}

@@

\textcolor{red}{And last, but not least significant to report, one of the great things about PhD is that the student will be able to conduct its research in the future. In that direction, we can say that with the methods proposed here and targeted to tackle the energy sector, there exists a vast field of future applications and developments, using different renewable sources. We can mention here biomass, wind, or even hybrid generation, with different mathematical models and requirements; and including smart grids, or electrical systems in general. Few research has been done until now, and the scenario is auspicious to do it.}
%besides the fact that the goal of a PhD is to contribute to the body of human research,
